peter_models

### 2024-12-15 peter_models.qmd
updating notebooks

  ggplot() +
    # Add vertical line at OR = 1
    geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +
    # Add points and error bars
    geom_point(aes(x = or_data_sig_renamed[,1], 
                   y = reorder(rownames(or_data_sig_renamed), or_data_sig_renamed[,1])), 
              size = 4, color = "blue") +
    geom_errorbarh(aes(xmin = or_data_sig[,2], 
                       xmax = or_data_sig[,3],
                       y = reorder(rownames(or_data_sig_renamed), or_data_sig_renamed[,1])),
                   height = 0.3, color = "black") +
    # Customize theme
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 6, color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
      axis.title.x = element_text(size = 12, face = "bold"),
      axis.title.y = element_text(size = 12, face = "bold"),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.margin = margin(1, 1, 1, 1, "cm"),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 9)
    ) +
    # Add labels
    labs(
      title = "Significant Variables with Confidence Intervals",
      x = "Odds Ratio",
      y = "Variables"
    )

@@

>>>>

  ggplot() +
    # Add vertical line at OR = 1
    geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +
    # Add points and error bars
    geom_point(aes(x = or_data_sig_renamed[,1], 
                   y = reorder(rownames(or_data_sig_renamed), or_data_sig_renamed[,1])), 
              size = 4, color = "blue") +
    geom_errorbarh(aes(xmin = or_data_sig[,2], 
                       xmax = or_data_sig[,3],
                       y = reorder(rownames(or_data_sig_renamed), or_data_sig_renamed[,1])),
                   height = 0.3, color = "black") +
    # Customize theme
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 6, color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
      axis.title.x = element_text(size = 12, face = "bold"),
      axis.title.y = element_text(size = 12, face = "bold"),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.margin = margin(1, 1, 1, 1, "cm"),
      legend.text = element_text(size = 8),
      legend.title = element_text(size = 9)
    ) +
    # Add labels
    labs(
      title = "Significant Variables with Confidence Intervals",
      x = "Odds Ratio",
      y = "Variables",
      caption = "Note: Some variable levels are excluded due to filtering for significant variables. \n To view the reference level for each variable group, please see the below table."
    )

@@

Table of Reference Levels

| Variable Group                              | Reference Level            |
|---------------------------------------------|----------------------------|
| Education                                   | No college experience      |
| Gender                                      | Man                        |
| Age                                         | 18-29 years old            |
| Race                                        | White                      |
| Importance of Racial Belonging              | Not At All Important       |
| Interaction Term: Racial Belonging & Gender | Male, Not At All Important |
